
    \begin{abstract_basarim}
    {Cuma 11:15-11:30}
    {BASARIM2022}
    {Oda: 202}
    {Muhammad A. Sasongko, Milind Chabbi, Paul H. J. Kelly, Didem Unat}
    {COMDETECTIVE $^{+}$: An Inter-Thread Communication Analyzer for AMD Multicores}
    {%
    Muhammad Aditya SASONGKO$^{1}$, Milind CHABBI$^{2}$, Paul H. J. KELLY$^{3}$, Didem UNAT$^{1}$}
    {%
    }
    {%
    $^1$ Koç University - İstanbul, Turkey\newline{}$^2$ Scalable Machines Research - California, USA\newline{}$^3$ Imperial College - London, UK}
    Abstract-AMD Processors have become more widely used in recent years due to the high performance yet low power consumption of the Ryzen series. Along with the increasing popularity of this processor series, there is also a rising need for profiling tools that can identify performance bottlenecks with low overheads in these machines. One common source of performance bottlenecks in multithreaded programs running on multicore systems is inter-thread communication.\newline We propose ComDETECTIVE ${ }^{+}$, an inter-thread communication analyzer that leverages the existing hardware features in AMD processors to support low-overhead detection of communications. It employs the instruction-based sampling (IBS) facility available in current AMD CPU cores to sample memory accesses, and debug registers to intercept communications involving the sampled memory accesses. In addition to detecting communications, COMDETECTIVE ${ }^{+}$also differentiates the communications into true sharing and false sharing, and attributes the communications to their locations in source code. We perform an experimental study to evaluate the accuracy, time, and memory overheads of this tool. Our tool exhibits high accuracy while introducing $2.8 \times$ runtime and $1.92 \times$ memory overheads, which are much lower than the overheads of existing cycle-accurate simulators and code instrumentation-based tools. 
    
            \textbf{Index Terms} \newline{}PMUs, performance analysis, multicore
    \end{abstract_basarim}
    